### 2018-11-04 Sections/cryptowars.tex
minor

In general, Eve will probe into the optical channel that Alice and Bob use to communicate. She send her own states into Alice’s system, which will reflect off the same apparatus Alice uses used to encode her signal. Eve's states can be imprinted upon some information about the encoding used by Alice, when Eve measures them. She can then use the result of this measurement, combined with some operation on the Alice's signals to make a best estimate of the quantum state that Alice sent to Bob, thus giving her some non-negligible information mutual with the key\cite{PhysRevA.97.042335}.

>>>>

In general, Eve probes into the optical channel that Alice and Bob use to communicate. She send her own states into Alice's system, which will reflect off the same apparatus Alice uses used to encode her signal. Eve's states can be imprinted upon some information about the encoding used by Alice, when Eve measures them. She can then use the result of this measurement, combined with some operation on the Alice's signals to make a best estimate of the quantum state that Alice sent to Bob, thus giving her some non-negligible information mutual with the key\cite{PhysRevA.97.042335}.
